pyTopoComplexity: A Python package for topographic complexity analysis

### 2024-08-23 JOSS/paper.rmd

To address this gap, we have developed an open-source Python toolkit called **pyTopoComplexity**. This toolkit 
offers computationally efficient and easily customizable implementations for performing and visualizing the results 
of 2D-CWT, fractal dimension, and rugosity index calculations (see Table 1\autoref{tab:1}). Additionally, **pyTopoComplexity** 
includes a module for calculating the Terrain Position Index (TPI), a widely used metric that is considered effective 
in geomorphology research [@Newman2018; @Deumlich2010; @Liu2011]. The TPI is also often used alongside rugosity index 
calculations in marine geological and ecological analyses [@Wilson2007; @Walbridge2018].

>>>>

To address this gap, we have developed an open-source Python toolkit called **pyTopoComplexity**. This toolkit 
offers computationally efficient and easily customizable implementations for performing and visualizing the results 
of 2D-CWT, fractal dimension, and rugosity index calculations (see Table 1\autoref{tab:1}). Additionally, **pyTopoComplexity** 
includes a module for calculating the Terrain Position Index (TPI), a widely used metric that is considered effective 
in geomorphology research [@Newman2018; @Deumlich2010; @Liu2011] and often used alongside Rugosity Index in marine 
geological and ecological studies [@Wilson2007; @Walbridge2018].
